|

### 2020-07-15 manuscript_1.0.Rmd
Found the bug on the implementation. The random number generator (sander's) is not thread safe. The problem is solved only for the interactions function. Must either adapt the RNG or change the engine.

---
title: |
  | Learning can mediate both badges of status and individual recognition
author:
  - name: Andrés E. Quiñones
    affiliation: "1"
  - name: C. Daniel Cadena
    affiliation: "1"
  - name: Olof Leimar
    affiliation: "2"
  - name: Redouan Bshary
    affiliation: "3"
address:
  - code: "1"
    address: Laboratorio de Biología Evolutiva de Vertebrados, Departamento de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia
  - code: "2"
    address: Department of Zoology, Stockholm University, Stockholm, Sweden
  - code: "3"
    address: Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland
date: "`r format(Sys.time(), '%B %d, %Y')`"
bibliography: SocialMorphCue.bib
header-includes: 
  - \usepackage{float}
  - \usepackage{setspace}\doublespacing
  - \linespread{2}
  - \usepackage{lineno}
  - \linenumbers
spacing: double
abstract: My abstract which has to be long enough to take multiple
  lines otherwise one does not see the effect of single-spacing.
keywords: "My keywords"
fig_caption: yes
keep_tex: yes
fontsize: 12pt
linespread: 2
output: pdf_document
---

@@

For social animals the outcome of interactions with conspecifics is an important 
determinant of fitness. Irrespective of whether such interactions are of cooperative or competitive nature, individual's actions will partly determine their success in the reproductive arena. However, the best action for an invidual might vary depending on it's 
own conditions, and on who they are interacting with. Thus, an individual making their action dependent on information about interacting partners is typically adaptive [@quinones_Negotiation_2016].The source of this information however is far from trivial. In some cases interacting
partners (signallers) might be 'willing' to provide accurate information, but in 
others it might be in their own interest to conceal information [@johnstone_Recognition_1997],
or to provide erroneous information. Typically, in a given context, some proportion of 
individuals will be interested in broadcasting accurate information, and some others 
in hiding it. Take for instance an interaction between two individuals where one can help the other. Given some conditions, the donor will be interested in helping a related individual. So for a relative of the donor, broadcasting kinship is advantageous; while for an unrelated
individual, conceling the lack of kinship will be better. This same pattern applies to 
many aspects social life such as finding mates, feeding offspring, dominance relationships and aggressive interactions. In dominance and aggressive interactions an important 
information to make actions dependent on is interacting partners fighting ability, 
which is sometimes refered to as Resource Holding Potential (RHP) [@parker_Assesment_1974] , or simply quality. Stable communication systems can evolve where a signal conveys quality can be 
evolutionarily stable whenever the signal imposes a fitness cost which increases with the quality of an individual

>>>>

---
title: |
  | Learning can mediate both badges of status and individual recognition
author:
  - Andrés E. Quiñones^[Laboratorio de Biología Evolutiva de Vertebrados, Departamento de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia]
  - C. Daniel Cadena^[Laboratorio de Biología Evolutiva de Vertebrados, Departamento de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia]
  - Olof Leimar^[Department of Zoology, Stockholm University, Stockholm, Sweden]
  - Redouan Bshary^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland]
date: "`r format(Sys.time(), '%B %d, %Y')`"
bibliography: SocialMorphCue.bib
style: C:\Users\andre\Zotero\styles\elife.csl
header-includes: 
  - \usepackage{float}
  - \usepackage{setspace}\doublespacing
  - \linespread{2}
  - \usepackage{lineno}
  - \linenumbers
spacing: double
abstract: My abstract which has to be long enough to take multiple
  lines otherwise one does not see the effect of single-spacing.
keywords: "My keywords"
fig_caption: yes
keep_tex: yes
fontsize: 12pt
linespread: 2
output: pdf_document
---

@@

For social animals the outcome of interactions with con-specifics is an important 
determinant of fitness. Irrespective of whether such interactions are of cooperative 
or competitive nature, individual's actions and their partners will partly determine 
their success in the reproductive arena. However, the best action for an individual 
might vary depending on it's own conditions, and with whom they interact. 
Thus, an individual making their action dependent on information about interacting 
partners is typically adaptive [@quinones_Negotiation_2016].
The source of this information however is far from trivial. 
In some cases interacting partners (signalers) might be 'willing' to provide accurate
information, but in others it might be in their own interest to conceal information
[@johnstone_Recognition_1997], or to provide erroneous information [@johnstone_Badges_1993]. 
Typically, in a given context, some proportion of individuals will be interested 
in broadcasting accurate information, and some others in hiding it. 
Take for instance an interaction between two individuals where one can help the other. 
Given some conditions of cost and benefits, the donor will be interested in helping 
a related individual. So for a relative of the donor, 
broadcasting kinship is advantageous; while for an unrelated individual, 
concealing the lack of kinship will be better. This same pattern applies to 
many aspects of social life such as finding mates, feeding offspring, dominance relationships 
and aggressive interactions. In dominance and aggressive interactions an important 
information to make actions dependent on is interacting partners fighting ability, 
which is sometimes referred to as Resource Holding Potential (RHP) [@parker_Assessment_1974], 
or as we will here simply quality. This responsiveness to the quality of the partner is achieved in
communication systems such as badges of status (BS), where an arbitrary signal conveys quality. 
BS can be evolutionarily stable whenever the signal imposes a fitness cost which 
decreases with the quality of an individual  [@botero_Evolution_2010; @johnstone_Badges_1993]. 
So, low quality individuals can't afford the cost of the signal, 
and it's no longer in their interest to fake quality. 
The cost of the honest signal is a more general principle of communications systems, 
usually referred to as the handicap principle [@grafen_Biological_1990; @zahavi_Mate_1975]. 
An alternative system of communication is one where individuals gather and store information
about each individual they interact with. This information, directly collected by 
each individual, should reliably allow them to react adaptively to the 
quality difference with their opponent. This type of assessment strategy is often referred to as 
individual recognition [IR, @whitfield_Plumage_1986]. Evidently, IR is restricted to 
certain interaction structures, individuals are limited by cognitive adaptations in how many
individuals they can recognize and track. Thus, IR and BS have been assumed to be alternative
communication systems fulfilling the same function, but expected to evolve in populations 
under different interaction structures [@dale_Signaling_2001; @sheehan_There_2016].
